Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-12-24 Manuscript/Ms.Rmd
adding a relevant ref
organising ideas for results

\textbf{Miguel Á. Collado$^{1}$} \orcidlink{0000-0002-4216-317X} \textbf{Jose B. Lanuza$^{2}$} \orcidlink{0000-0002-0287-409X} \textbf{Ferran Sayol$^{3}$} \orcidlink{0000-0003-3540-7487} \textbf{and Ignasi Bartomeus$^{2}$} \orcidlink{0000-0001-7893-4389}

@@

\textbf{Author for correspondence:}

@@

@@

For the `r nlevels(factor(unique(d$Species)))` bee species, brain size scaled allometrically with body size (Bayesian R$^2$ = `r r2`). However, there were considerable variability in brain size relative to the body across species (Figure S1). Considering this association, the species with the largest and smallest brains relative to the body were the American bee *`r largest_encephalisation`* and the European bee *`r lowest_encephalisation`*, respectively.

Mention how this is constrained by phylogenetic relationship but there is still large variability.

Histogram

Model

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,fig.align="center", fig.height=6, fig.width=7, fig.cap="\\textbf{Figure S2.}", fig.pos="p", out.width="100%"}

>>>>

\orcidlink{0000-0002-4216-317X} \textbf{Jose B. Lanuza$^{1}$} \textbf{Miguel Á. Collado$^{2}$}  \orcidlink{0000-0002-0287-409X} \textbf{Ferran Sayol$^{3}$} \orcidlink{0000-0003-3540-7487} \textbf{and Ignasi Bartomeus$^{1}$} \orcidlink{0000-0001-7893-4389}

@@

\textbf{Author for correspondence: barragansljose@gmail.com}

@@

https://www.biorxiv.org/content/10.1101/2022.12.09.519739v1

@@

#Read phylo signal
phylo = read_rds("../Data/Processing/phylo_signal.rds")
lambda = round(phylo$lambda, 2)
```

Our dataset showed that brain size scaled allometrically with body size (Bayesian R$^2$ = `r r2`). As expected, this allometric relationship was constrained by the evolutive history of the species (phylogenetic signal of relative brain size, $\lambda$ = `r lambda`; *P* < 0.01). However, we found considerable variability in relative brain size (Figure S1; Figure 2A) within and across the different taxonomic groups (i.e., genera and subfamily level).

Explain now habitat preference trends by species (Figure 2B)

Explain overall habitat preference patterns (Figure 3)

Explain main models and model by continent (Figure 4 and Figure S2)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,fig.align="center", fig.height=6, fig.width=8, fig.cap="\\textbf{Figure S2.}", fig.pos="p", out.width="100%"}
